\chapter{BACKGROUND AND LITERATURE REVIEW}

% (20\% of Report Length)

% a. Must be paraphrased without plagiarizing

% b. Must include the base papers\cite{Adhikari2020Dec}, and support the rationale of the project

% c. Must highlight the strengths and shortcomings of the works performed by other authors

\section{Background Study}
In today's rapidly evolving PC hardware market, the complexity of selecting and configuring PC components has surged. Users often face challenges in identifying compatible parts and optimizing their configurations. The proposed project seeks to address this issue by leveraging Bootstrap, a powerful front-end web framework, to develop an intuitive and user-friendly online platform. The objective is to simplify the process of building PC configurations by offering a structured interface, real-time updates, and seamless compatibility checks, ultimately empowering users to create their ideal PC setups efficiently.\\
By leveraging the power of Build Wizard, users can confidently navigate the vast array of PC components, unleash their creativity, and embark on the journey of building their dream computer systems.

\section{Literature Review}
The field of computer science and technology has advanced rapidly over the years, leading to significant developments in the design and assembly of personal computers (PCs). One crucial aspect of building a PC is selecting the right components, such as processors, graphics cards, memory modules, and storage devices.\\
In this research paper, the authors present PC Builder Hero, a virtual reality (VR) game that allows users to experience the process of building a custom personal computer (PC) in a safe and immersive environment. The primary objective of the game is to increase awareness and curiosity about the inner components and workings of computers. By utilizing VR technology, the game aims to provide users with a hands-on experience of building a PC, without the risk of costly mistakes. Users are able to select virtual computer components and track the price of their built computer, as well as monitor the accumulation of static electricity over time. The game challenges users to find a balance between component specifications and overall price, while adhering to proper PC building procedures. The paper provides detailed information on the design and implementation of a high-fidelity prototype of the game, along with the results and implications of an informal early testing phase\cite{slovikosky2019pc}.
The objective of this project is to assist users in buying or upgrading custom-branded PCs by providing recent information about computer components and automatically filtering for compatibility. The implementation involves web scraping for component information, building a database to store the data, and creating a user-friendly web page for component display and compatibility checks. The database is updated daily to ensure up-to-date information. The main contribution of this project is the automatic detection of component compatibility, which is particularly helpful for first-time buyers who may be hesitant to build their own PC\cite{romero2021implementing}.
A custom-built PC is assembled to cater to specific user needs. Internationally, there are many e-stores available for users that offer them the option to build and order their systems according to their requirements. However, the COVID-19 pandemic in 2020 led to cancellations of international shipments, highlighting the local market's deficiency in fulfilling the demands of custom-built PC users. In this paper, a generic architecture for an e-store called Nice PC Maker (NPM) is proposed and designed to address this issue. The architecture facilitates users with custom-build PC options, as well as additional features like pre-built system purchasing and PC component purchasing. The implementation of the architectural design utilizes WooCommerce product builders in WordPress. The configuration of this generic architecture for a local client not only helps them enhance their business but also provides users with the convenience of obtaining their desired systems\cite{khursheed2023nice}.